\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-17 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

From \eqref{ExplicitdPhidt}, it follows that $\frac{\differential}{\differential t}\Phi \leq 0$, i.e., $\Phi$ is non-increasing along the flow generated by \eqref{TransformedPDEivp}. Furthermore, \eqref{lastequality} tells us that $\frac{\differential}{\differential t}\Phi = 0$ if and only if 
$$\bm{M}^{-1}\bm{\Gamma}\bm{\eta} + \bm{\ell}_{\bm{\eta}} = 0$$

>>>>

From \eqref{ExplicitdPhidt}, it follows that $\frac{\differential}{\differential t}\Phi \leq 0$, i.e., $\Phi$ is non-increasing along the flow generated by \eqref{TransformedPDEivp}. Furthermore, \eqref{lastequality} tells us that $\frac{\differential}{\differential t}\Phi = 0$ if and only if 
$$\bm{M}^{-1}\bm{\Gamma}\bm{\eta} + \bm{\ell}_{\bm{\eta}} = 0,$$
i.e., $\Phi$ is stationary if and only if $\tilde{\rho}$ has $\bm{\eta}$ marginal $\int\tilde{\rho}\:\differential\bm{\xi} \propto \exp\left(-\bm{\eta}^{\top}\bm{M}^{-1}\bm{\Gamma}\bm{\eta}\right)$. Following the steps as in \cite[Appendix E.1]{krichene2020global}, this is achieved at the stationary solution of \eqref{NewPDE} with $\bm{\xi}$ marginal $\int\tilde{\rho}\:\differential\bm{\eta} \propto \exp\left(-2U(\bm{\xi})\right)$. In other words, the stationary solution of \eqref{NewPDE} must be of the form 
$$\tilde{\rho}_{\infty}(\bm{\xi},\bm{\eta}) \propto \exp\left(-2U(\bm{\xi})+\bm{\eta}^{\top}\bm{M}^{-1}\bm{\Gamma}\bm{\eta}\right),$$
and is exactly where $\frac{\differential}{\differential t}\Phi = 0$. Therefore, $\frac{\differential}{\differential t}\Phi < 0$ along the transient solution of \eqref{NewPDE}, and $=0$ at the stationary solution of \eqref{NewPDE}.
